Shallow EDSLs and Object-Oriented Programming

### 2016-06-20 paper/sections/Modularity.tex

To make it clear, Figure~\ref{code:compare} give the corresponding OO implementation using composition
and inheritance respectively.
\begin{figure}
\begin{tabular}{lll}
\begin{minipage}{.17\textwidth}
\begin{lstlisting}
trait T {
  def f: Int
  def g: Int
}
class A extends T {
  def f = g
  def g = 0
}
\end{lstlisting}
\end{minipage}
&
\begin{minipage}{.17\textwidth}
\begin{lstlisting}
class B(a: A) extends T {
  def f = a.f
  def g = 1
}
new B(new A).f// 0
\end{lstlisting}
\end{minipage}
&
\begin{minipage}{.17\textwidth}
\begin{lstlisting}
class B extends A {
  override def g = 1
}
(new B).f// 1
\end{lstlisting}
\end{minipage}
\end{tabular}
\caption{Composition (left) vs Inheritance (right)}
\label{code:compare}
\end{figure}
In the case of inheritance, calling \lstinline{f} will execute the overridden \lstinline{g}
as \lstinline{this} points to \lstinline{B} rather than \lstinline{A}.
For compositions, a method can not be reused if when the implementation of what
they depend on changes like \lstinline{f} in \lstinline{A}, even if the logic holds.
OO languages provide these two options for reusing code.

>>>>

To make it clear, Figure~\ref{code:compare} give the corresponding OO implementation using composition
and inheritance respectively.
\begin{figure}
\setlength{\tabcolsep}{1pt}
\begin{tabular}{lll}
\begin{minipage}[b]{.15\textwidth}
\begin{lstlisting}
trait T {
  def f: Int
  def g: Int
}
class A
    extends T {
  def f = g
  def g = 0
}
\end{lstlisting}
\end{minipage}
&
\begin{minipage}[b]{.15\textwidth}
\begin{lstlisting}
// Composition
class B(a: A) extends T {
  def f = a.f
  def g = 1
}
B(A).f // 0
\end{lstlisting}
\end{minipage}
&
\begin{minipage}[b]{.2\textwidth}
\begin{lstlisting}
// Inheritance
class B extends A {
  override def g = 1
}
B.f // 1
\end{lstlisting}
\end{minipage}
\end{tabular}
\caption{Composition vs Inheritance}
\label{code:compare}
\end{figure}
In the case of inheritance, calling \lstinline{f} will execute the overridden \lstinline{g}
as \lstinline{this} points to \lstinline{B} rather than \lstinline{A}.
For compositions, a method can not be reused if when the implementation of what
they depend on changes like \lstinline{f} in \lstinline{A}, even if the logic holds.
OO languages provide these two options for reusing code.
